Data-Driven Modelling \& \\ Forecasting of Chaotic Systems

### 2022-01-16 Gandhi_Project_Report/draft5.tex
Many graphs added and comments added. Edits of Ch.5. Starting to prep to add Grammarly back in

\section{Practical Limitations to Takens' Theorem}

@@

It turns out that $\bigcap_{i<n}X_{n,i}(\overline{u})$ is identically equal to $X_n(\overline{u})$ that we had defined earlier \textbf{(Cite.)}. This will lead to a result (for. e.g., \cite{manjunath2013echo}) that  \textit{$g$ being a topological contraction is equivalent to the existence of a exactly one entire solution.}

@@

\begin{Theorem}\label{Thm_CompactExistence}
 Let $g$ be a driven system.  If $X$ is compact, then for each input $\overline{u}$, there exists at least one solution to the driven system $g(\ldotp, x)$
\end{Theorem}
\begin{proof}
  May be found in \cite{kloeden2011nonautonomous, manjunath2014dynamics, manjunath2013echo}
\end{proof}

@@

\ednote{RC introduced a bit abruptly} Reservoir Computing(RC) refers to a machine learning approach in which input is mapped onto a different, but higher dimensional, space through a system called the reservoir after which a readout measuring the reservoir state is trained.
In the majority of Reservoir Computing(RC) literature \textbf{(Cite)}, a notion of forgetting the states of the reservoir asymptotically is often used.  
Concepts like the echo state property(ESP) and  fading memory \cite{boyd1985fading} are two of these.  
If $g$ possesses the ESP (equivalent in our context to the USP \textbf{(Cite)}), we are guaranteed that the whole of an input's left-infinite history will exactly determine the current system state; i.e. there is only ever the possibility of a single reachable state at a given instance of time \cite{jaeger2001echo,Manju_2020}.
% \cite{Manju_ESP}.
Beyond forgetting the past states, the ESP is also often discussed in terms of a stability property that plays a key role in the robustness of recurrent neural networks(RNN).
The concept, termed input-related stability~\cite{manjunath2020stability}, refers the phenomenon of nearby inputs creating responses (solutions) close to one another.

@@

 \begin{Theorem}
  For a compactly driven system, a causal mapping $H$ exists if and only if $g$ has the USP. 
\end{Theorem}
\begin{proof}
  See~\cite[Th.3]{manjunath2013echo}.
\end{proof}

@@

So far it is not clear if the USP alone ensures the ability to causally embedding a dynamical system and we mention that a driving function $g$ cannot just be chosen in a frivolous manner. This could possibly complicate our work. \ednote{Dié lees vreemd}

@@

%To achieve a causal embedding embedding not just a causal mapping, it is undesirable to choose a function $g$ that quenches the temporal structure in $u$ by contracting to such a degree that the ability to recover information from the original system is lost completely.
In the above example(\ref{ex_halfux}), the input's temporal variation could not be related to the reachable set as $X_U$ only consisted of a single element; little, if not no, information is encoded.
To obtain a suitably complex function $g$, it is thus desired that the reachable set of a driven system  be large enough to relate to the input. 
This is true even for embedding  the inverse-limit space of a dynamical system. \textbf{(B: Expand or refer?)}

@@

\begin{Theorem}
If we let $G_T:Y_T\to{Y_T}$ be a map defined by the relation $(x_{n-1},x_n)\mapsto(x_n,x_{n-1})$, then $G_T$ is well-defined (and this results holds even in the absence of $g$ possessing over the USP)  
\end{Theorem}
\begin{proof}
  \textbf{See .....................}
\end{proof}

@@

\begin{figure}[ht]
  \includegraphics[scale=0.35]{_Nonlinearity_Fig_response.eps}
  \centering
\captionof{figure}{A coordinate of a simulated solution $(x_0,x_1,\ldots,x_{5000})$ of a RNN  plotted in red (with parameter $\alpha=0.99$ (where $g$ has the USP) and blue ($a=1$ and $\alpha=1.05$ where $g$ does not have the USP) while the matrices $A$ and $B$ are randomly generated, and $B$ has unit spectral radius. Reproduced from \cite{Manju_Nonlinearity}.}
\label{fig:memloss_conttime} 
\end{figure} \ednote{This graph with the black line does not immediately make sense}

@@

%\begin{Theorem}\label{thm_usp-contr-uap}  The following statements are equivalent:  \vspace{-8mm}  \begin{enumerate}[noitemsep, label=\roman*.]    \item $g$ has the USP.    \item $g$ is a topological contraction.    \item $g$ has the UAP.  \end{enumerate\end{Theorem}\begin{proof}  May be found in \cite[Th.1]{Manju_Nonlinearity}\end{proof}

@@

\begin{Theorem}
  [\bf Causal Embedding Theorem (adopted from \cite{Supp})]
  % {\bf (Causal Embedding Theorem.)}
 \label{Thm_CET}
	Let $g$ be a driven system with SI-invertibility and the USP. Let $h$ denote the universal semi-conjugacy and $H_2(\overleftarrow{u}) := (h(r\overleftarrow{u}),h(\overleftarrow{u}))$, where $r$ is the right-shift map. 
 Let $(\widehat{U}_T, \widehat{T})$  be the inverse-limit system of a dynamical system $(U,T)$. 
 Then the restriction of $H_2$ to $\widehat{U}_T$ is a topological semi-conjugacy between the inverse-limit system $(\widehat{U}_T, \widehat{T})$ 
and the induced dynamical system  $(Y_T,G_T)$, i.e., the following diagram commutes
\begin{equation} \label{comm_H_CET}
\psset{arrows=->, arrowinset=0.25, linewidth=0.6pt, nodesep=3pt, labelsep=2pt, rowsep=0.7cm, colsep = 1.1cm, shortput =tablr}
 \everypsbox{\scriptstyle}
 \begin{psmatrix}
 \widehat{U}_T & \widehat{U}_T\\%
 Y_T &  Y_T.
 %%%
%  \ncline{1,1}{1,2}^{\widehat{T}} \ncline{1,1}{2,1} <{H_2}
%  \ncline{1,2}{2,2} > {H_2}
%  \ncline{2,1}{2,2}^{G_T}
 \end{psmatrix}
 \end{equation}
or in other words, $(Y_T, G_T)$ is a factor of  $(\widehat{U}_T, \widehat{T})$. Further, if $T:U \to U$ is a homeomorphism, 
then $H_2$ embeds $\widehat{U}_T$ in $X_U \times X_U$, and hence $(Y_T, G_T)$ is conjugate to $(\widehat{U}_T, \widehat{T})$.
\end{Theorem}
\begin{proof}
  May be found as the proof of~\cite[Th.4]{Supp}
\end{proof}

Recall that $H_2$ maps an entire left-infinite solution sequence from $\Psi$ \ednote{Check}to an element in $X\times{X}$. 
\ednote{Rephrase}We are drawing nearer and nearer to our principal target and our results carry more and more weight. Since if learn $G_T$ we would have learnt $\widehat{T}$ and since $\widehat{T}$ is an extension of $T$, we would have learnt $T$ as well.

\ednote{Why is theorem on inverse-limit system taken out?}
%\begin{Theorem} Graph \ref{Scomm_h} is exactly the inverse-limit system $(\hat{U}, \hat{T})$.    \end{Theorem}

@@

%\begin{Theorem}
 %   $(Y_T, G_T)$ is semi-conjugate to $(\widehat{U}, \widehat{T})$.
%\end{Theorem}
%\begin{proof}
%  See \cite[Th.3, Th.4]{manunath2021universal}
%\end{proof}

@@

Finally, we note that although $G_T$ exists with SI-invertibility, we need USP  otherwise the driven states has to be running for all time since the driven states would not have forgotten its past states.

% Below is reproduced a pictorial representation of the relationship between different entities and properties. \textbf{(Cite SIG_25May)}
% Below is reproduced a pictorial representation of the relationship between the different entities and their properties.

\begin{figure}[ht]
  \includegraphics[scale=0.3]{_summarypictorial.eps}
  \centering
  \label{fig:fig_pictorialSummary}
\end{figure}
\ednote{M: Please put a caption on this figure and cite the figure in the main text}

@@

In \cite{manjunath2021universal} it is illustrated in an empirical fashion in that the map $G_T$ describes dynamics which are less functionally complex than that of $T$ or of the map $\Phi_{2d,\theta}$. This is done by implementing a Recurrent Neural Network (RNN), which is discussed in~\ref{ch5}. \ednote{(B: Should I add in that we'll be using Pearson coefficient?)}

@@

\begin{Theorem}
  When $x_n$ and $x_{n-1}$ are successive points on a solution obtained for input-orbit of $T$ $\{u_n\}$, then the map $\Gamma: X\times{X}\to{U}$ defined by $(x_{n-1},x_n)\mapsto{u_n}$ exists whenever $G_T$ exists 
\end{Theorem}
\begin{proof}
  See \cite[Th. 3c]{manjunath2021universal}.
\end{proof}

@@

Secondly, the function $\Gamma$ is known to be stable. Learning $\Gamma$ makes use of equations \ref{eqns_from_data} which in turn employs the driven system $g$ possessing the USP, and offers distinct advantages with regards to stability in the presence of perturbation. It is desirable that inputs that differ only slightly would have only ‘slight’ effects on the output of the system. Moreover, one would hope to prevent numerical errors originating from input and measurement noise (see~\cite[Th. 5]{manjunath2021universal}). 
As the data fed into the system is a function of both the input given and the parameters of the system itself (i.e. the value a, $\alpha$ in $\tanh$), we exploit both input-related and parameter-related stability. Both these notions are defined by way of the continuity of an encoding map of an input and design parameter respectively in \cite{manjunath2020stability}.\

@@

\begin{figure}[ht]
  \includegraphics[scale=0.25]{_autovsdriven.eps}
  \centering
  \label{fig:learningFailure}
  \captionof{figure}{Illustrating empirically the importance of global dissipativity. Plotted below are the three principal components of randomly initiated points(blue) of a learnt version of $G_T$ versus the trajectory $(x_{n-1}, x_n)$(red) of driven states obtained from the Fractal Dream Attractor's data~\ref{Thomas_Attractor}). }
\end{figure}
\ednote{nice figure: Please rescale the figure and also you do not have to state that code was borrowed. So I have omitted that in the caption. Please put a caption to the figure and then cite in the text. }

Thirdly, whenever we learn a chaotic map on a set (here $Y_T$), as we had remarked in the disadvantages of Takens delay embedding a little noise would mean that the learnt system would accept arguments out of the set, so we will have a map $G_T^+$ acting on $Y_T^+$, and since $Y_T$ may not be an attractor of $G_T$ this could lead to errors. To circumvent this if the driven system with a saturation function is used, then we can ensure that there exists an attractor $A$ of the map that implements $G_T$ indirectly via $g$ containing $Y_T^+$. This prevents from large errors occuring since the dynamics is confined to $A$.  We refer to \cite{Supp} for details where this is referred to as the global dissipativity of $g$.

In essence, global dissipativity prevents large numerical errors due to the noise in input data. If a system is not globally dissipative, neglibly small errors result could lead to major errors which thus induce predictions to fail utterly. If one learns $G_T$ directly, we are in danger of replicating the problems arising for Takens.

>>>>

\section{Practical Limitations to Takens' Theorem}\label{sect_takenslimits}

@@

It turns out that $\bigcap_{i<n}X_{n,i}(\overline{u})$ is identically equal to $X_n(\overline{u})$ that we had defined earlier \ednote{(Insert citations.)}. This will lead to a result (for. e.g., \cite{manjunath2013echo}) that  \textit{$g$ being a topological contraction is equivalent to the existence of a exactly one entire solution.}

@@

\begin{Theorem}\label{Thm_CompactExistence}
 Let $g$ be a driven system.  If $X$ is compact, then for each input $\overline{u}$, there exists at least one solution to the driven system $g(\ldotp, x)$
\end{Theorem}
{\bf Proof.}  May be found in \cite{kloeden2011nonautonomous, manjunath2014dynamics, manjunath2013echo}

@@

\ednote{B: RC introduced a bit abruptly. Adjust.} Reservoir Computing(RC) refers to a machine learning approach in which input is mapped onto a different, but higher dimensional, space through a system called the reservoir after which a readout measuring the reservoir state is trained.
In the majority of Reservoir Computing(RC) literature \textbf{(Cite)}, a notion of forgetting the states of the reservoir asymptotically is often used.  
Concepts like the echo state property(ESP) and  fading memory \cite{boyd1985fading} are two of these.  
If $g$ possesses the ESP (equivalent in our context to the USP \textbf{(Cite)}), we are guaranteed that the whole of an input's left-infinite history will exactly determine the current system state; i.e. there is only ever the possibility of a single reachable state at a given instance of time \cite{jaeger2001echo,Manju_2020}.
% \cite{Manju_ESP}.
Beyond forgetting the past states, the ESP is also often discussed in terms of a stability property that plays a key role in the robustness of recurrent neural networks(RNN).
The concept, termed input-related stability~\cite{manjunath2020stability}, refers the phenomenon of nearby inputs creating responses (solutions) close to one another.

@@

 \begin{Theorem}
  For a compactly driven system, a causal mapping $H$ exists if and only if $g$ has the USP. 
\end{Theorem}
{\bf Proof.}  See~\cite[Th.3]{manjunath2013echo}.

@@

So far it is not clear if the USP alone ensures the ability to causally embedding a dynamical system and we mention that a driving function $g$ cannot just be chosen in a frivolous manner. This could possibly complicate our work. %\ednote{B: Grammarly}

@@

%To achieve a causal embedding embedding not just a causal mapping, it is undesirable to choose a function $g$ that quenches the temporal structure in $u$ by contracting to such a degree that the ability to recover information from the original system is lost completely.
In the above example(\ref{ex_halfux}), the input's temporal variation could not be related to the reachable set as $X_U$ only consisted of a single element; little, if not no, information is encoded.
To obtain a suitably complex function $g$, it is thus desired that the reachable set of a driven system  be large enough to relate to the input. 
This is true even for embedding  the inverse-limit space of a dynamical system. \ednote{B: Expand or refer?}

@@

\begin{Theorem}\label{Thm_GT_Exists}
  For an SI-invertible driven system $g$ and a dynamical system $(U,T)$, the map $G_T: Y_T \to Y_T$ defined by the relation $(x_{n-1},x_n) \mapsto (x_n,x_{n+1})$ is well-defined. 
  (This results holds even in the absence of $g$ possessing over the USP) 
  % Moreover, the mapping $(x_{n-1},x_n) \mapsto u_{n}$ is well-defined when $x_{n-1}$ and $x_n$ are successive points on a solution obtained for an input  $\{u_n\}$ that is an orbit of $T$.
  \end{Theorem}
  {\bf Proof.} See~\cite[Th.3]{Supp}

@@

\begin{figure}[ht]
  \includegraphics[scale=0.35]{_Nonlinearity_Fig_response.eps}
  \centering
\captionof{figure}{A coordinate of a simulated solution $(x_0,x_1,\ldots,x_{5000})$ of a RNN  plotted in red (with parameter $\alpha=0.99$ (where $g$ has the USP) and blue ($a=1$ and $\alpha=1.05$ where $g$ does not have the USP) while the matrices $A$ and $B$ are randomly generated, and $B$ has unit spectral radius. 
Reproduced from \cite{Manju_Nonlinearity}. }
\label{fig:memloss_conttime} 
\end{figure} 
\ednote{B: How can I explain the black line? I don't think this makes sense to the reader immediately.}

@@

%\begin{Theorem}\label{thm_usp-contr-uap}  The following statements are equivalent:  \vspace{-8mm}  \begin{enumerate}[noitemsep, label=\roman*.]    \item $g$ has the USP.    \item $g$ is a topological contraction.    \item $g$ has the UAP.  \end{enumerate\end{Theorem} {\bf Proof.}  May be found in \cite[Th.1]{Manju_Nonlinearity}

@@

\begin{Theorem}
  [\bf Causal Embedding Theorem (adopted from \cite{Supp})]
  % {\bf (Causal Embedding Theorem.)}
 \label{Thm_CET}
	Let $g$ be a driven system with SI-invertibility and the USP. Let $h$ denote the universal semi-conjugacy and $H_2(\overleftarrow{u}) := (h(r\overleftarrow{u}),h(\overleftarrow{u}))$, where $r$ is the right-shift map. 
 Let $(\widehat{U}_T, \widehat{T})$  be the inverse-limit system of a dynamical system $(U,T)$. 
 Then the restriction of $H_2$ to $\widehat{U}_T$ is a topological semi-conjugacy between the inverse-limit system $(\widehat{U}_T, \widehat{T})$ 
and the induced dynamical system  $(Y_T,G_T)$, i.e., the following diagram commutes
\begin{equation} \label{comm_H_CET}
\psset{arrows=->, arrowinset=0.25, linewidth=0.6pt, nodesep=3pt, labelsep=2pt, rowsep=0.7cm, colsep = 1.1cm, shortput =tablr}
 \everypsbox{\scriptstyle}
 \begin{psmatrix}
 \widehat{U}_T & \widehat{U}_T\\%
 Y_T &  Y_T.
 %%%
%  \ncline{1,1}{1,2}^{\widehat{T}} \ncline{1,1}{2,1} <{H_2}
%  \ncline{1,2}{2,2} > {H_2}
%  \ncline{2,1}{2,2}^{G_T}
 \end{psmatrix}
 \end{equation}
or in other words, $(Y_T, G_T)$ is a factor of  $(\widehat{U}_T, \widehat{T})$. Further, if $T:U \to U$ is a homeomorphism, 
then $H_2$ embeds $\widehat{U}_T$ in $X_U \times X_U$, and hence $(Y_T, G_T)$ is conjugate to $(\widehat{U}_T, \widehat{T})$.
\end{Theorem}
{\bf Proof.}  May be found as the proof of~\cite[Th.4]{Supp}

Recall that $H_2$ maps an entire left-infinite solution sequence from $\Psi$ to an element in $X\times{X}$. 
We are drawing nearer and nearer to our principal target and our results carry more and more weight: If we are able to learn $G_T$, we will also have learnt $\widehat{T}$; and since $\widehat{T}$ is an extension of $T$, we will have obtained $T$ as well.  %\ednote{B: Grammarly check}

%\begin{Theorem} Graph \ref{Scomm_h} is exactly the inverse-limit system $(\hat{U}, \hat{T})$.    \end{Theorem}

@@

%\begin{Theorem}
 %   $(Y_T, G_T)$ is semi-conjugate to $(\widehat{U}, \widehat{T})$.
%\end{Theorem}
% {\bf Proof.} See \cite[Th.3, Th.4]{manunath2021universal}

@@

Finally, we note that although $G_T$ exists with SI-invertibility, we need the USP as well(see \ref{fig_pictorialSummary} below for a visual illustration). If not, the driven states would have to be running for all time since they would not have forgotten their past states.

\begin{figure}[ht]
  \includegraphics[scale=0.3]{_summarypictorial.eps}
  \centering
  \captionof{figure}{Pictorial summary of results obtained up to now and how they overlap. Reproduced from \textbf{(Cite SIG-25May)} }
  \label{fig:fig_pictorialSummary}
\end{figure}

@@

In \cite{manjunath2021universal} it is illustrated in an empirical fashion in that the map $G_T$ describes dynamics which are less functionally complex than that of $T$ or of the map $\Phi_{2d,\theta}$. This is done by implementing a Recurrent Neural Network (RNN), which is discussed in~\ref{ch5}. \ednote{B: Should I add in that we'll be using Pearson coefficient?}

@@

\begin{Theorem}
  When $x_n$ and $x_{n-1}$ are successive points on a solution obtained for input-orbit of $T$ $\{u_n\}$, then the map $\Gamma: X\times{X}\to{U}$ defined by $(x_{n-1},x_n)\mapsto{u_n}$ exists whenever $G_T$ exists 
\end{Theorem}
{\bf Proof.}  See \cite[Th. 3c]{manjunath2021universal}.

@@

Secondly, the function $\Gamma$ is known to be stable. Learning $\Gamma$ makes use of equations \ref{eqns_from_data} which in turn employs the driven system $g$ possessing the USP, and offers distinct advantages with regards to stability in the presence of perturbation. It is desirable that inputs that differ only slightly would have only ‘slight’ effects on the output of the system. Moreover, one would hope to prevent numerical errors originating from input and measurement noise (see~\cite[Th. 5]{manjunath2021universal}). 
As the data fed into the system is a function of both the input given and the parameters of the system itself (i.e. the value a, $\alpha$ in $\tanh$), we exploit both input-related and parameter-related stability. Both these notions are defined by way of the continuity of an encoding map of an input and design parameter respectively in \cite{manjunath2020stability}.\ednote{B: Is this satisfactory?}

@@

Thirdly, learning a chaotic map on a set(here $Y_T$) with even a small measure of noise  means that the learnt system accepts arguments out of the set (Problems similar to Takens, cf.~\ref{sect_takenslimits}). 
We thus have a map $G_T^+$ acting on $Y_T^+$ and since $Y_T$ is not guaranteed to be an attractor of $G_T$ this could lead to errors.
If one learns $G_T$ directly, we are in danger of replicating the problems arising for Takens.  To see this, consider Fig.~\ref{fig:YtGtFailure}.

\begin{figure}[ht]
  \includegraphics[scale=0.25]{_YTerrors.eps}
  \centering
  \captionof{figure}{Diagram of potential errors developing when $G_T$ is learnt.}
  \label{fig:YtGtFailure}
\end{figure}

To circumvent this: if a driven system with a saturation function\ednote{B: What is a saturation function?} is used, we can indirectly (via $g$) ensure the existence of an attractor $A$ of the map which implements $G_T$, and containing $Y_T^+$.  \ednote{B: I'm not sure this sentence makes complete sense.}
By defining the dynamics to $A$, this prevents large errors from occuring.  
More details on the global dissipativity of $g$, as it is termed there, may be found in~\cite{Supp}.

\begin{figure}[ht]
  \includegraphics[scale=0.25]{_autovsdriven.eps}
  \centering
  \captionof{figure}{Illustrating empirically the importance of global dissipativity. Plotted below are the three principal components of randomly initiated points(blue) of a learnt version of $G_T$ versus the trajectory $(x_{n-1}, x_n)$(red) of driven states obtained from the Fractal Dream Attractor's data~\ref{Thomas_Attractor}). }
  \label{fig:learningFailure}
\end{figure}

In effect, global dissipativity prevents large numerical errors due to the noise in input data from arising (see Fig.~\ref{fig:learningFailure}). 
If a system is not globally dissipative, neglibly small errors could lead to major inaccuracy which thus induce predictions to utterly fail.

### 2022-01-16 Gandhi_Project_Report/draft6.tex
Many graphs added and comments added. Edits of Ch.5. Starting to prep to add Grammarly back in

  The authors of~\cite{manjunath2021universal} did not, however, consider the relationship between the inverse-limit space $\widehat{U}_T$ and the input $u_n=\theta(w_n)$ (where $\theta$ is our observable and $w_n$ the complete input), a concept we now explore.
  We may construct a delay-coordinate $v_n=[\theta(w_n), \theta(w_{n-1}), \ldots, \theta(w_{n-d})]^{T} = [u_n, u_{n-1}, \ldots, u_{n-d}]^T$
    to accordingly obtain a new dynamical system $(V,F)$ where $F$ is the map $F:v_n\mapsto{v_{n+1}}$. If $d$ is sufficiently large, we may apply Takens Embedding Theorem~\ref{Thm_Takens} to establish the existence of a topological conjugacy between the new system $(V,F)$ and the original system $(U,T)$.

  Using the same notation as before, we may construct a new conjugacy which now relates delay coordinates to one another.

  \begin{equation}\label{eqn_VFdelay}
    %  \[ 
        \psset{arrows=->, arrowinset=0.25, linewidth=0.6pt, nodesep=3pt, labelsep=2pt, rowsep=0.7cm, colsep = 1.1cm, shortput =tablr}
        \everypsbox{\scriptstyle}
        \begin{psmatrix}
        \widehat{V}_F  && \widehat{V}_F \\
        Y_F && Y_F \\
        %%%
       %  \ncline{1,1}{1,2}^{\widehat{F}} \ncline{1,1}{2,1} <{h}
       %  \ncline{1,2}{2,2} > {*}
       %  \ncline{2,1}{2,2}^{G_F}
        \end{psmatrix}
      %  \]
    \end{equation}

@@

\end{document}

>>>>

  The authors of~\cite{manjunath2021universal} did not, however, consider the relationship between the inverse-limit space $\widehat{U}_T$ and the input $u_n=\theta(w_n)$ (where $\theta$ is our observable and $w_n$ the complete input), a concept we now explore.

Let $(V,T)$ be a dynamical system with dynamics generated by the update equation $v_{n+1}=Tv_n$
Consider the case where the only available information is observations $\theta$ from an orbit of the map $T$ where $\theta:V\to\mathbb{R}$ is an observable. 
Our task is still to find some system topologically conjugate to $(V,T)$ so that we may use the datapoints $\theta(v_{0}),\theta(v_{1}),\ldots,\theta(v_{m})$ to predict the subsequent observations $\theta(v_{m+1}),\theta(v_{m+2}),\ldots$.

Applying the Takens embedding theorem, we may conclude that when an input from the delay-coordinate mapping $\Phi_{\theta,2d}(\theta(v_{n})) := (\theta(v_{n-2d}),\ldots,\theta(v_{n-1}),\theta(v_{n}))$ is fed to the driven system $g$ as the input $u_n$, 
there exists a homeomorphism $F_\theta: \Phi_{\theta,2d}(\theta(v_{n})) \mapsto \Phi_{\theta,2d}(\theta(v_{n+1}))$.

This may be stated alternatively as follows: If the inpute $u_n$ is of the form $u_n := \Phi_{\theta,2d}(\theta(v_{n}))$ and is fed to a driven system $g$ possessing both the USP and SI-invertibility, 
it follows from the Causal Embedding Theorem~\ref{Thm_CET} that the newly generated space $(Y_F,G_F)$ topologically conjugate to the inverse-limit space of $(\Phi_{\theta,2d}(V), F_\theta)$.
Moreover, we can forecast the values $u_n,u_{n+1},\ldots$ and $\theta(v_n), \theta(v_{n+1}),\ldots$ as well as having the guarantee that this embedding is stable when considered in terms of global dissipativity as discussed before.

\begin{equation}\label{eqn_VFdelay}
%  \[ 
    \psset{arrows=->, arrowinset=0.25, linewidth=0.6pt, nodesep=3pt, labelsep=2pt, rowsep=0.7cm, colsep = 1.1cm, shortput =tablr}
    \everypsbox{\scriptstyle}
    \begin{psmatrix}
    \widehat{\Phi}_{2d,\theta}  && \widehat{\Phi}_{2d,\theta} \\
    Y_F && Y_F \\
    %%%
    %  \ncline{1,1}{1,2}^{\widehat{F}_\theta} \ncline{1,1}{2,1} <{h}
    %  \ncline{1,2}{2,2} > {*}
    %  \ncline{2,1}{2,2}^{G_F}
    \end{psmatrix}
  %  \]
\end{equation}

%   We may construct a delay-coordinate $v_n=[\theta(w_n), \theta(w_{n-1}), \ldots, \theta(w_{n-d})]^{T} = [u_n, u_{n-1}, \ldots, u_{n-d}]^T$
%     to accordingly obtain a new dynamical system $(V,F)$ where $F$ is the map $F:v_n\mapsto{v_{n+1}}$. If $d$ is sufficiently large, we may apply Takens Embedding Theorem~\ref{Thm_Takens} to establish the existence of a topological conjugacy between the new system $(V,F)$ and the original system $(U,T)$.

%   Using the same notation as before, we may construct a new conjugacy which now relates delay coordinates to one another.

%   \begin{equation}\label{eqn_VFdelay}
%     %  \[ 
%         \psset{arrows=->, arrowinset=0.25, linewidth=0.6pt, nodesep=3pt, labelsep=2pt, rowsep=0.7cm, colsep = 1.1cm, shortput =tablr}
%         \everypsbox{\scriptstyle}
%         \begin{psmatrix}
%         \widehat{V}_F  && \widehat{V}_F \\
%         Y_F && Y_F \\
%         %%%
%        %  \ncline{1,1}{1,2}^{\widehat{F}} \ncline{1,1}{2,1} <{h}
%        %  \ncline{1,2}{2,2} > {*}
%        %  \ncline{2,1}{2,2}^{G_F}
%         \end{psmatrix}
%       %  \]
%     \end{equation}

@@

\bibliographystyle{pnas-new}
\bibliography{pnas}
\printbibliography
\end{document}
